LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-02-17 src/ms.tex
fix some alignment
add in description of requirement for quasi-circular binaries in amplitude modulation use case

We note that since the orbit averaging is carried out in Fourier space, this requires the frequency to be monochromatic and thus is only implemented in \lw{} for quasi-circular binaries (as eccentric systems emit at many frequency harmonics).

@@

\begin{equation}{}
\label{eq:signal}
    \begin{split}
        |\tilde{s}(f)|^2 = |&F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta) \\
        &+ F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
    \end{split}
\end{equation}
where $F_{+,\times}$ are the `plus' and `cross' antenna patterns of the LISA detector to the `plus' and `cross' strains, $h_{+,\times}$. Note throughout any parameters discussed with the subscript $x_{+,\times}$ refers to both $x_{+}$ and $x_{\times}$.

>>>>

\referee{We note that the amplitude modulation is only implemented in \lw{} for quasi-circular binaries to remain consistent with the calculation in \cite{Cornish2003}. Since the expected use case of LEGWORK is estimation of the detectability of large populations of mHz stellar-remnant binaries, for which predictions are uncertain by orders of magnitude in some cases, an extension of \cite{Cornish2003} which includes eccentric binaries is out of the scope of \lw{}.}

@@

\begin{equation}{}
\label{eq:signal}
    \begin{split}
        |\tilde{s}(f)|^2 = |&F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta) \\
        + &F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
    \end{split}
\end{equation}
where $F_{+,\times}$ are the `plus' and `cross' antenna patterns of the LISA detector to the `plus' and `cross' strains, $h_{+,\times}$. Note throughout any parameters discussed with the subscript $x_{+,\times}$ refers to both $x_{+}$ and $x_{\times}$.
